%% Master CV - Alejandro D'Ambrosio
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Alejandro D'Ambrosio - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Alejandro}{D'Ambrosio}
\address{Ciudad Autónoma de Buenos Aires, Argentina}{}{}
\phone[mobile]{+54 9 11 5175 8480}
\email{alejandro.dambrosio@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/aledambrosio}{LinkedIn}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Solutions Architect and technical leader with 18+ years building enterprise software across backend, web, and native mobile. I design production-grade architectures, raise engineering quality across teams, and have led delivery for large financial clients including Banco Galicia and OSDE. Deep expertise in Java and iOS/Swift, with cloud experience on Google Cloud and OpenShift, and a track record of leading 40+ developers while staying hands-on with research and PoCs.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Architecture \& Leadership}: Solution and software architecture (backend, web, native/hybrid mobile); technical leadership of teams up to 40+ developers; mentoring and career-path definition.

\item \textbf{Backend \& Enterprise Java}: Java, Spring, Spring Boot, Hibernate, Struts, Drools, OSWorkflow, JUnit; microservices on OpenShift.

\item \textbf{Mobile}: Native iOS in Swift (banking/homebanking apps), REST/OData integration, omnichannel; hybrid mobile with Ionic.

\item \textbf{Web \& Cloud}: React, Node.js/Express, JavaScript/jQuery; Google Cloud (Cloud Run, Firebase, networking); CI/CD and quality tooling.

\item \textbf{Data \& Agile}: DB2 and relational SQL, PL/SQL, MongoDB, Firebase; Scrum and Kanban delivery.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Flux IT: Solutions Architect ---
\item{\cventry{2023--Present}{Solutions Architect}{Flux IT}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Solution architecture across web, backend, and native/hybrid mobile for enterprise clients.
    \item Drive architecture, research, innovation, team building, and software quality.
\end{itemize}}}

\vspace{3pt}

% --- Flux IT: Technical Leader ---
\item{\cventry{2021--2023}{Technical Leader}{Flux IT}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Led 40+ developers across Java backend, native iOS/Android, and React web for a single enterprise client.
    \item Set quality standards and good engineering practices; defined developers' career paths.
    \item Supported client team leaders on team health, technical innovation, and new ideas.
\end{itemize}}}

\vspace{3pt}

% --- Flux IT: Team Technical Leader ---
\item{\cventry{2019--2021}{Team Technical Leader}{Flux IT (Banco Galicia)}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Led a 4-developer team building microservices for a new architecture of the bank's customer-service channels.
    \item Stack: OpenShift, Java, Spring Boot.
\end{itemize}}}

\vspace{3pt}

% --- Flux IT: iOS Tech Lead / Software IT Architect ---
\item{\cventry{2016--2019}{iOS Tech Lead \& Software IT Architect}{Flux IT (Banco Galicia)}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Technical reference for the iOS team building the Banco Galicia homebanking app (project Galaxia).
    \item Owned mobile architecture components and development guidelines; coordinated a 4-person iOS team.
    \item Stack: Swift, storyboards, REST web services, OData, omnichannel.
\end{itemize}}}

\vspace{3pt}

% --- Flux IT: Java Developer ---
\item{\cventry{2011--2016}{Java Developer}{Flux IT (OSDE)}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Enterprise Java web and BPM development for OSDE (healthcare): new developments, performance analysis, and database tuning.
    \item Stack: OSWorkflow, Drools, Struts, Spring, Hibernate, ServiceMix, DB2.
\end{itemize}}}

\vspace{3pt}

% --- Globant ---
\item{\cventry{2008--2010}{Software Engineer}{Globant}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Software engineering for Gilbarco Veeder-Root (fuel dispenser / point-of-sale simulators) and Electronic Arts (BattleForge portal).
    \item Tools: J2SE, Delphi, Rational ClearCase/ClearQuest, Vignette, Spring.
\end{itemize}}}

\vspace{3pt}

% --- Earlier roles (condensed) ---
\item{\cventry{2006--2008}{Java Developer}{TIVIT / Synapsis (PSA Peugeot Citroën, Edelnor, Codensa)}{Buenos Aires, Argentina}{}{\vspace{1pt}
\begin{itemize}
    \item Tech lead of the Argentina team for PSA Peugeot Citroën (Paris HQ coordination); web apps with JSF/Spring/Hibernate and PL/SQL.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{1997--2016}{Engineer's degree, Systems Engineering}{Universidad Tecnológica Nacional (UTN)}{Buenos Aires, Argentina}{}{}}

\vspace{3pt}

\item{\cventry{1997--2009}{Analyst, Information Systems}{Universidad Tecnológica Nacional (UTN)}{Buenos Aires, Argentina}{}{}}

\vspace{3pt}

\item{\cventry{2019--2020}{Ontological Coaching / Leadership}{CAYZEN Global}{Buenos Aires, Argentina}{}{}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (professional working), French (elementary).
\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item Scrum: Roles; Google Cloud Skill Badges (Serverless on Cloud Run, Cloud Networking, Serverless with Firebase).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
